A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-30 12_conclusions_future_work.tex
dash in contour-parallel

\section{Conclusion and future work}
In this paper we have introduced a framework for computing contour parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas.
Our framework is flexible, demonstrated by the several beading schemes which emulate existing techniques.
The computation times of our framework are on par with the state-of-the-art library for performing offsets of non-adaptive bead width.
Our framework is stable: small local changes in the outline shape cause only small changes in the toolpath.

>>>>

\section{Conclusion and future work}
In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas.
Our framework is flexible, demonstrated by the several beading schemes which emulate existing techniques.
The computation times of our framework are on par with the state-of-the-art library for performing offsets of non-adaptive bead width.
Our framework is stable: small local changes in the outline shape cause only small changes in the toolpath.

### 2019-08-30 2_related_work.tex
dash in contour-parallel

% basic toolpath strategies and their variations
Direction parallel and contour parallel are two basic toolpath strategies.
Direction parallel (or zig-zag) toolpath fills an arbitrarily shaped contour with a set of parallel, equally spaced line segments.
These parallel segments are linked at one of their extremities, to avoid frequent stop and restart.
Contour parallel toolpath typically consists of a set of equally spaced offset contours from the slice boundary.
\citeauthor{steuben2016implicit} presented implicit slicing and made an interpretation of 2D contour computing as evaluating intersections in 3D~\cite{steuben2016implicit}.
A strategy to connect the parallel offsets was introduced in~\cite{KUIPERS2019CAD}. This approach however introduces sharp turns.
To reduce the number of sharp turns, and thereby enable faster motions, \citeauthor{Zhao2016} proposed to use Fermat spiral to cover the contour~\cite{Zhao2016}. 
Spiral toolpaths have also been applied to machining~\cite{Held2009,Huang2017}.
One of the problems with contour parallel toolpath is that it tends to leave gaps within the slices (\cref{intro_wedge} top).
This is due to the fact that the offset contour meets around the medial axis and the remaining space might not exactly match the (constant) deposition width.
To avoid problems with such gaps, hybrid approaches that combine direction and contour parallel are often used~\cite{Mcmains2000DETC,Jin2013adaptive}.
Close to the slice boundary, there are a few contour parallel curves, while in the interior there is a zig-zag pattern.
For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them, the basic strategies can be applied~\cite{Ding2014,Jin2017RCIM}.
Alternative toolpath patterns, seen also in CNC machining, include space-filling curves~\cite{Cox1994CAD,Griffiths1994,Shaikh2016}.

% the idea, and (some of) the most related work
Our approach to reduce under- and over-filling is to deposit material with a varying width.
This allows the opportunity to locally match the nonuniform space between adjacent paths, and thus to ensure a better filling of the area.
Material extrusion with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
However, we note that the range of possible widths is not unlimited.
For instance, printing a width that is triple the nozzle diameter is challenging.
Our method to reduce underfilling is related to the work by \citeauthor{kao1998optimal}~\cite{kao1998optimal}.
Instead of uniform offsetting, they produced adaptive offsetting toolpaths based on the geometry skeleton. 
Skeleton was also used in~\cite{Jin2017RCIM} to construct a skeleton-based path for alleviating under- and over-filling in contour parallel toolpath. 
The adaptive offsetting approach by \citeauthor{kao1998optimal} handles simple geometry where there are no branches in the medial axis.
An extension was proposed by \citeauthor{Ding2016a} to handle complex shapes~\cite{Ding2016a}.
For this purpose, they made use of the medial axis to decompose the slice into a set of simple geometries.
This extension, however, inherits a problem in the original method.
From any point in the geometry skeleton to the boundary, the number of contours is constant.
Since the distance may vary considerably, this strategy leads to a toolpath with widths that may differ by a factor of two or more, which is challenging for FDM prinring.
\citeauthor{Jin2017JMS} proposed to add a toolpath with varying width along the skeleton, while leaving other paths unchanged~\cite{Jin2017JMS}.
The resulting variation of width in the central is pronounced (\cref{intro_wedge} middle).
In this paper we propose a novel scheme to distribute the width variations from center to boundary, and thus limits the width variation (\cref{intro_wedge} bottom).

>>>>

% basic toolpath strategies and their variations
Direction parallel and contour-parallel are two basic toolpath strategies.
Direction parallel (or zig-zag) toolpath fills an arbitrarily shaped contour with a set of parallel, equally spaced line segments.
These parallel segments are linked at one of their extremities, to avoid frequent stop and restart.
Contour-parallel toolpath typically consists of a set of equally spaced offset contours from the slice boundary.
\citeauthor{steuben2016implicit} presented implicit slicing and made an interpretation of 2D contour computing as evaluating intersections in 3D~\cite{steuben2016implicit}.
A strategy to connect the parallel offsets was introduced in~\cite{KUIPERS2019CAD}. This approach however introduces sharp turns.
To reduce the number of sharp turns, and thereby enable faster motions, \citeauthor{Zhao2016} proposed to use Fermat spiral to cover the contour~\cite{Zhao2016}. 
Spiral toolpaths have also been applied to machining~\cite{Held2009,Huang2017}.
One of the problems with contour-parallel toolpath is that it tends to leave gaps within the slices (\cref{intro_wedge} top).
This is due to the fact that the offset contour meets around the medial axis and the remaining space might not exactly match the (constant) deposition width.
To avoid problems with such gaps, hybrid approaches that combine direction and contour-parallel are often used~\cite{Mcmains2000DETC,Jin2013adaptive}.
Close to the slice boundary, there are a few contour-parallel curves, while in the interior there is a zig-zag pattern.
For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them, the basic strategies can be applied~\cite{Ding2014,Jin2017RCIM}.
Alternative toolpath patterns, seen also in CNC machining, include space-filling curves~\cite{Cox1994CAD,Griffiths1994,Shaikh2016}.

% the idea, and (some of) the most related work
Our approach to reduce under- and over-filling is to deposit material with a varying width.
This allows the opportunity to locally match the nonuniform space between adjacent paths, and thus to ensure a better filling of the area.
Material extrusion with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
However, we note that the range of possible widths is not unlimited.
For instance, printing a width that is triple the nozzle diameter is challenging.
Our method to reduce underfilling is related to the work by \citeauthor{kao1998optimal}~\cite{kao1998optimal}.
Instead of uniform offsetting, they produced adaptive offsetting toolpaths based on the geometry skeleton. 
Skeleton was also used in~\cite{Jin2017RCIM} to construct a skeleton-based path for alleviating under- and over-filling in contour-parallel toolpath. 
The adaptive offsetting approach by \citeauthor{kao1998optimal} handles simple geometry where there are no branches in the medial axis.
An extension was proposed by \citeauthor{Ding2016a} to handle complex shapes~\cite{Ding2016a}.
For this purpose, they made use of the medial axis to decompose the slice into a set of simple geometries.
This extension, however, inherits a problem in the original method.
From any point in the geometry skeleton to the boundary, the number of contours is constant.
Since the distance may vary considerably, this strategy leads to a toolpath with widths that may differ by a factor of two or more, which is challenging for FDM prinring.
\citeauthor{Jin2017JMS} proposed to add a toolpath with varying width along the skeleton, while leaving other paths unchanged~\cite{Jin2017JMS}.
The resulting variation of width in the central is pronounced (\cref{intro_wedge} middle).
In this paper we propose a novel scheme to distribute the width variations from center to boundary, and thus limits the width variation (\cref{intro_wedge} bottom).

### 2019-08-30 4_method.tex
dash in contour-parallel

Our method starts with computing the skeleton of the input polygon based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour parallel toolpaths~\cite{eiamsa2003toward}. 
We visualize the skeleton as the union of cones (UoC) (\cref{sec_surface_construction}), by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (\cref{overview_uoc}).
Contour parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of planar planes at equally spaced heights (\cref{3d_surface_overview}\subref{overview_outline}-\subref{overview_uniform_paths}).

>>>>

Our method starts with computing the skeleton of the input polygon based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour-parallel toolpaths~\cite{eiamsa2003toward}. 
We visualize the skeleton as the union of cones (UoC) (\cref{sec_surface_construction}), by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (\cref{overview_uoc}).
Contour-parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of planar planes at equally spaced heights (\cref{3d_surface_overview}\subref{overview_outline}-\subref{overview_uniform_paths}).
